SAYCAM Main analyses from bounding box outputs

### 2020-06-17 analysis/analyses_fullset_redo_from_bb_outputs.Rmd
add code to redo center cropping from bb outputs

## OP bounding box outputs
```{r}
op_file_dir = here::here("data/op_outputs_per_vid/")
op_files = dir(op_file_dir)
```

@@

@@

### Regualrize vid names
```{r}
all_vid_data <- all_vid_data %>%
  rowwise() %>%
  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])
```

### Get rid of vids to exclude from allocentric file
```{r}
all_vid_data <- all_vid_data %>%
  mutate(vid_name_old = vid_name) %>%
  select(-vid_name) %>%
  filter(!vid_name_cleaned %in% to_exclude$vid_name)
```

@@

@@

### Plot face/hand detections by age by child
```{r}
ggplot(wide_uncropped,
       aes(x=age_day_bin, y=prop,
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend =
  ylab('Proportion Detections') +
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) +
  theme_few(base_size=18) +
  ggthemes::scale_color_solarized(name = "") +
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")
```

@@

# Basic analysis #2: Location variability

## Preprocessing
### Load metadata 
```{r}
# meta
load(here::here('data/preprocessed_data/saycam_metadata.RData'))
```

>>>>

## OP bounding box outputs
```{r}
op_file_dir = here::here("data/op_outputs_per_vid/")
op_files = dir(op_file_dir)
# op_files = op_files [1] # for testing
```

@@

## Crop out detections from outer edges of frames; do so at video level.
```{r}
# cropping paramts
limit_lower =.2
limit_upper =.8
# vid params
y_max = 480
x_max = 640

reload_data=TRUE
if (reload_data){
vid_index = 0
for (vid_file in op_files) {

   # to check progress
   vid_index = vid_index + 1
   if ((vid_index %% 100)==0) { print (vid_file) }

   # get vid level data
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)

    # don't bother for these files
   if (!this_vid_data$vid_name[1] %in% to_exclude$vid_name){

    # for renormalizing y's vids which were run differently this time
   if (this_vid_data$child_id[1]=='Y'){
     this_vid_data <- this_vid_data %>%
      mutate(top = top/y_max, height = height/y_max, left = left/x_max, width = width/x_max)
   }

   # now get vid level data
   summary_vid_data_center <- this_vid_data %>%
     mutate(num_frames = length(unique(frame))) %>% # count frames
     mutate(center_y = top + height/2, center_x = left + width/2) %>% # get center_x and y
     filter(center_y<(limit_upper) & center_x<(limit_upper) & center_y>(limit_lower) & center_x>(limit_lower)) %>%   # filter within parameters
     group_by(frame, child_id, vid_name, num_frames, age_days) %>% # group at frame level first
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0) %>%
     group_by(child_id, vid_name, age_days, num_frames) %>% # now at the video level
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected)) # count how many faces/hands

   # compile vid-level summaries 
   if (vid_index == 1){
     all_vid_data_center <- summary_vid_data_center
   }
   else if (vid_index > 1) {
   all_vid_data_center <- all_vid_data_center %>%
     full_join(summary_vid_data_center)
   }
}
}
}

```

@@

### Regualrize vid names & get rid of vids to exclude from allocentric file
```{r}
all_vid_data <- all_vid_data %>%
  rowwise() %>%
  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])

all_vid_data <- all_vid_data %>%
  mutate(vid_name_old = vid_name) %>%
  select(-vid_name) %>%
  filter(!vid_name_cleaned %in% to_exclude$vid_name)
```

```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

# function to return prfs
 return_prf_short = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
 }

```

```{R}
 ## load gold sample annotations
 load(here('data/data_cogsci/gold_sample_annotations2020-01-31.RData')) # gold_sample, pre-filtered

gold_sample_frames <- gold_sample %>%
  select(vid_name, frame)

gold_sample_vids <- unique(gold_sample_frames$vid_name)
```

```{r}
# redo gold sample 
if (reload_data){
vid_index = 0
for (vid_file in op_files) {

   # to check progress
   vid_index = vid_index + 1
   if ((vid_index %% 100)==0) { print (vid_file) }

   # get vid level data
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)
   this_vid_name <- this_vid_data$vid_name[1]

   # if it's one of the vids from gold sample
   if (this_vid_name %in% unique(gold_sample_frames$vid_name)){
   # and not excluded
   if (!this_vid_name %in% to_exclude$vid_name){

   frames_to_get <- gold_sample_frames %>%
     filter(vid_name == this_vid_name)

   # now get vid level data
   gold_sample_op <- this_vid_data %>%
     filter(frame %in% frames_to_get$frame) %>%
     group_by(frame, vid_name) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)

   # compile vid-level summaries 
   if (vid_index == 1){
     all_gold_sample_frames_op <- gold_sample_op
   }
   else if (vid_index > 1) {
   all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
     full_join(gold_sample_op)
   }
}
}
}
}
```

```{r}

 ## evaluate detectors
 gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))

 ## output prfs
 face_performance = return_prf_short(gold_sample$face_eval_ketan)
 hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
```

@@

```{r}
summary_by_age_center <- all_vid_data_center %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)

```

@@

```{r}
wide_center <- summary_by_age_center %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "centered",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
  filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
```

### Plot face/hand detections by age by child
```{r}
ggplot(wide_uncropped,
       aes(x=age_day_bin, y=prop,
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend =
  geom_smooth(data = wide_center, aes(weight = num_frames_total), show.legend = FALSE, 
              lty = 2, span=10, se = FALSE) +
  ylab('Proportion Detections') +
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) +
  theme_few(base_size=18) +
  ggthemes::scale_color_solarized(name = "") +
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")
```

@@

# Basic analysis #2: Location variability
## Preprocessing
### Load metadata 
```{r}
# meta
load(here::here('data/preprocessed_data/saycam_metadata.RData'))
```
